Irt plot extra

### 2022-03-24 manuscript.Rmd
Redundant Code blocks are removed

#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,reshape, ggsci,networkD3, webshot,ggtext)
webshot::install_phantomjs()
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")
devtools::install_github("unDocUMeantIt/koRpus")
koRpus::install.koRpus.lang(lang=c("en"))

@@

---
nocite: |
  `r cite_r("references.bib")`
  [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
  [@horne1976self][@roenneberg2003life][@Olivier.2016][@buysse1989pittsburgh][@Xie.2021][@bossini2006sensibilita]
---

@@

```{r relscale, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#This chunk holds code for Relevant scales table in the manuscript
relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")

```{r reltab2, eval=FALSE, include=FALSE, results='asis'}
relevant.scale.data %>% 
apa_table(landscape =T,caption ="List of instruments measuring related constucts to LEBA", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data))))

@@

```{r rafel, eval=FALSE, include=FALSE}
# In addition to the LEBA questionnaire, which is subject of the current study, we assessed other variables and items which were not included in the present analysis. This comprised various sleep-related measures, i.e., sleep disturbances and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011], sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [MCTQ version for adults and adolescents @roenneberg2003life] plus sleep environment [@Olivier.2016]. Furthermore, we included a light sensitivity questionnaire (photophobia vs. photophilia) [@Wu.2017] and self-reported pubertal stage assessment [@Petersen.1988] for participants younger than 18 years of age. Moreover, we incorporated custom items on meal timing and caffeine consumption in the “workday vs. free day” structure of the MCTQ sleep-wake regulation. Example items are: “On workdays I usually have my first meal at __:__”, “On free days I usually have my last meal at __:__”, and “On workdays I usually drink my first caffeinated drink at __:__”.

@@

```{r Manuflowchart, eval=FALSE, include=FALSE}
#This chunk holds code for the work flow chart of the data analysis

Flowchart1 <- grViz("digraph my_flowchart{

                    graph [fontname = Helvetica,layout = dot,fontsize = 45 ]

                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 20, height = 3, 
                    fixedsize = true,fontsize = 45]

                    A[label = 'Initial development of 48 items'] 
                    B[label = 'Large scale survey: first round (n=428)']
                    C[label = 'Initial item analysis']
                    D[label = 'Exploratory factor analysis (48 items; n=428)']

                    E[label = 
                    <Factor Identification Method<br/>Scree plot<br/>Minimum average partial method<br/>Hull method>
                    ]

                    F[label = 'Reliability analysis on latent stucture obtained in EFA (n=428)']
                    G[label = 'Large scale survey: second round (n=262)']

                    H[label = 'Confirmatory factor analysis ( n=262)']

                    I[label = 'Reliability analysis on latent stucture obtained in CFA (n=262)']

                    K[label = 'LEBA long format: 23-item', style = filled, fillcolor = Beige]

                    L[label = 'Measurement invariance analysis (n=262)']
                    M[label = 'Semantic analysis (n=262)']
                    N[label = 'Item Response Theory based analysis on the combined sample (n=690)']

                    O[label = 'LEBA short format: 18-item', style = filled, fillcolor = Beige]

                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
                     A ->B
                     B ->C
                     C ->D
                     D ->E
                     E ->F
                    F ->G
                     G ->H
                     H ->I
                     I ->K

                    K->L
                    L ->M
                    M ->N
                    N->O

}")

library(jpeg)
export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Figures/Flowchart1.jpeg", dpi = 600)

```{r participantmap, include =F}

countries <- as.data.frame(tz_tibble[,1])
countries <- as.data.frame(countries[-1,])

colnames(countries) <- "TZ"
countries.2 <- as.data.frame(str_split_fixed(countries$TZ, "-", 2))
countries.2[ ,1][ countries.2[ , 1 ] == "United States " ] <- "USA"
countries.2[ ,1][ countries.2[ , 1 ] == "United Kingdom " ] <- "UK"
countries.2[ ,1][ countries.2[ , 1 ] == "Germany " ] <- "Germany"
countries.2[ ,1][ countries.2[ , 1 ] == "India "  ] <- "India" 
countries.2[ ,1][ countries.2[ , 1 ] == "France "  ] <- "France" 
countries.2[ ,1][ countries.2[ , 1 ] == "Switzerland " ] <- "Switzerland"
countries.2[ ,1][ countries.2[ , 1 ] == "Brazil "  ] <- "Brazil"
countries.2[ ,1][ countries.2[ , 1 ] == "Netherlands " ] <- "Netherlands"
countries.2[ ,1][ countries.2[ , 1 ] == "Canada "  ] <- "Canada" 
countries.2[ ,1][ countries.2[ , 1 ] == "Poland " ] <- "Poland"

country_name <- as.data.frame(unique(countries.2[,1]))
country_name.2 <- (country_name[1:10,])

thismap = map_data("world")

# Set colors
colors <- scales::hue_pal()(10)
thismap <- mutate(thismap, fill = ifelse(region %in% country_name.2, 
                                         sample(colors, 10), "white"))
thismap <- within(thismap, fill[region == 'Canada'] <- '#FF62BC')
thismap <- within(thismap, fill[region == 'Brazil'] <- '#D89000')
thismap <- within(thismap, fill[region == 'USA'] <- '#00BFC4')
thismap <- within(thismap, fill[region == 'UK'] <- 'blue')
thismap <- within(thismap, fill[region == 'Germany'] <- 'Green')
thismap <- within(thismap, fill[region == 'Netherlands'] <- '#A3A500')
thismap <- within(thismap, fill[region == 'Poland'] <- 'Pink')
thismap <- within(thismap, fill[region == 'France'] <- 'Orange')
thismap <- within(thismap, fill[region == 'Switzerland'] <- 'purple')

label.data <-thismap[thismap$region %in% country_name.2,]

USA <- subset(label.data, region == "USA")
UK <- subset(label.data, region == "UK")
Germany <- subset(label.data, region == "Germany")
India <- subset(label.data, region == "India")
France <- subset(label.data, region == "France")
Switzerland <- subset(label.data, region == "Switzerland")
Brazil <- subset(label.data, region == "Brazil")
Netherlands <- subset(label.data, region == "Netherlands")
Canada <- subset(label.data, region == "Canada")
Poland <- subset(label.data, region == "Poland")

label.data.2 <- rbind(USA[386,],UK[1,],Germany[1,],India[327,],France[1,],
                      Switzerland[1,],Brazil[33,],Netherlands[1,],Canada[5000,],Poland[1,])

label.data.2[1,1] <- -100
label.data.2[1,2] <- 40
label.data.2[2,2] <- 52
label.data.2[9,2] <- 55
label.data.2[7,2] <- -9
label.data.2[7,1] <- -48
label.data.2[4,2] <- 25
label.data.2[4,1] <- 84

label.data.2[5,2] <- 46
label.data.2[5,1] <- 6
label.data.2[8,2] <- 51

distribution <- ggplot(thismap, aes(long, lat, fill = fill, group=group)) + 
  geom_polygon(colour="gray", size =.3) +  
  scale_fill_identity()+apatheme+ theme(
    axis.text.x = element_blank(),
                                        axis.text.y = element_blank(),
                                        axis.title.x = element_blank(),
                                        axis.title.y = element_blank(),
                                        plot.title = element_blank(),
                                        axis.line.x = element_blank(),
                                        axis.line.y = element_blank(),
                                        axis.ticks = element_blank())+
  # xlab("Longitude") + ylab("Latitude")+
  ggrepel::geom_text_repel(data= label.data.2,aes(x=long, y= lat, label=region),inherit.aes = F,
            color = "darkblue", fontface = "bold", stat = 'identity',
            position = "identity")

ggsave("Figures/distribution.png", distribution, width = 12, height = 6, dpi = 600, bg ="white")

@@

```{r rafael2, eval=FALSE, include=FALSE}
# Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey.
# - `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
# - `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
# - `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
# - `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
# - `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
# - `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
# - `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
# - `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
# - `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
# - `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
```

@@

full.tab.2 <- full.tab[24:48,] %>% 
  gt()

@@

full.tab.2 %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "grey",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("Summary Descriptives (n =690)"),
    subtitle = md("Items 24-48 ")) %>% 
#create groups of columns
tab_spanner(
  label = "Item",
  columns = Item:Stem
) %>%
  cols_align(
    align = "left",
    columns = Item:Stem
  ) %>% 
  tab_spanner(
    label = "Summary Statistics",
    columns = mean:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Item = ("LEBA  Items"),
  Stem = ("Stem"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = mean:Always
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Item,
    palette = "ggthemes::fivethirtyeight"
  ) %>% tab_options(
    table.font.size = px(14L)) %>% 
  cols_width(
    Stem ~ px(200)) %>% 
gtsave("Figures/gt_full_p2.png",vwidth = 6000)

@@

S1 Fig summarizes the univariate descriptive statistics for the 48 items among  EFA sample (n =`r nrow(EFA.data)`.  Our data violated both univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970]. Multivariate skew was  `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p <0.001). Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018]. The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`. However, no item was discarded based on descriptive statistics or item analysis.

@@

Scree plot ( Figure \@ref(fig:efa-plot)) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Table \@ref(tab:map)) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Sup.Table \@ref(tab:MinResTab)). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. Supplimentary figure 1 depicts the data distribution and endorsement pattern for the included 25 items. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)(D)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Sup.Table \@ref(tab:sixFacTab)).

@@

```{r simulation, eval=FALSE, include=FALSE}
#This chunk holds codes for simulating Standard error for the accepted CFA model

library("simsem")
pop.model <- "F1 =~ a1*item16 + .95*item36 + a2*item17
                 F2 =~ .87*item11 + .85*item10 + .74*item12+ .60*item07+ .50*Ritem08+ .49*item09
                 F3 =~  .78*item27+ .77*item03+ .68*item40 + .13*item30 + .20*item41
                 F4 =~ a3*item32 + .63*item35 + .33*item38+ a4*item33 
                 F5 =~ .80*item46+ .53*item45+ .36*item25+ .30*item04+ .22*item01 
                       a1==a2
                       a3==a4
                item30 ~~ .82*item41
F1~~1*F1
F2~~1*F2
F3~~1*F3
F4~~1*F4
F5~~1*F5
"

sam.model <- "F1 =~ a1*item16 + item36 + a2*item17
                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                 F3 =~  item27+ item3+ item40 + item30 + item41
                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
                 F5 =~ item46+ item45+ item25+ item4+ item1 
                       a1==a2
                       a3==a4
                item30 ~~  item41
                       "

sim.300 <- sim(200, model = sam.model, n =200, generate = pop.model, lavaanfun = "lavaan", auto.var =T, auto.fix.first =F, seed = 123)
summary(simulation)
summaryParam(simulation, detail =T, alpha = .05)

#power should be higher than .80, average CI width should be lower than .15
#Estimate standard error bias

SD.Bias <- (summaryParam(simulation)[3]-summaryParam(simulation)[2])/summaryParam(simulation)[3]
```

>>>>

#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr, paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,reshape, ggsci,ggtext)
webshot::install_phantomjs()
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")
devtools::install_github("unDocUMeantIt/koRpus")
koRpus::install.koRpus.lang(lang=c("en"))

@@

---
nocite: |
  `r cite_r("references.bib")`
  [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
  [@horne1976self][@roenneberg2003life][@buysse1989pittsburgh][@Xie.2021][@bossini2006sensibilita][@grandner2014development]
---

@@

@@

@@

@@

@@

full.tab.2 <- full.tab[25:48,] %>% 
  gt()

@@

full.tab.2 %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "grey",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("Summary Descriptives (n =690)"),
    subtitle = md("Items 25-48 ")) %>% 
#create groups of columns
tab_spanner(
  label = "Item",
  columns = Item:Stem
) %>%
  cols_align(
    align = "left",
    columns = Item:Stem
  ) %>% 
  tab_spanner(
    label = "Summary Statistics",
    columns = mean:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Item = ("LEBA  Items"),
  Stem = ("Stem"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = mean:Always
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Item,
    palette = "ggthemes::fivethirtyeight"
  ) %>% tab_options(
    table.font.size = px(14L)) %>% 
  cols_width(
    Stem ~ px(200)) %>% 
gtsave("Figures/gt_full_p2.png",vwidth = 6000)

@@

Supplementary Fig1 summarizes the univariate descriptive statistics for the 48 items among  EFA sample (n =`r nrow(EFA.data)`.  Our data violated both univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970]. Multivariate skew was  `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p <0.001). Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018]. The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`. However, no item was discarded based on descriptive statistics or item analysis.

@@

Scree plot ( Figure \@ref(fig:efa-plot) B) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Supplementary Table 2) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print) D) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Sup.Table \@ref(tab:MinResTab)). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. Supplimentary figure 1 depicts the data distribution and endorsement pattern for the included 25 items. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)(D)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Supplementary Table 3)).

@@
